Extended Abstract

### 2021-05-04 paper/paper.tex
Add abstract

\documentclass[sigplan,review,screen]{acmart}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\end{document}

>>>>

\documentclass[sigplan,screen,review]{acmart}

\usepackage{todonotes}

\newcommand{\picalc}{$\pi$-calculus}
\newcommand{\Picalc}{$\pi$-Calculus}

\title{Extended Abstract}
\subtitle{Co-Contextual Type Inference for the Linear \Picalc{} in Agda}

\author{Uma Zalakain}
\affiliation{University of Glasgow}
\email{u.zalakain.1@research.gla.ac.uk}

\author{Ornela Dardha}
\affiliation{University of Glasgow}
\email{ornela.dardha@glasgow.ac.uk}

@@

\begin{abstract}
  The linear \picalc{} is an important substructural type system for the \picalc{}:
  it is a common target for the encoding of session-typed languages \todo{cite},
  and it in direct correspondence with classical linear logic \todo{cite}.

  Type inference for the linear \picalc{} comes with its own challenges:
  for one, processes themselves are untyped, and thus typing constraints only apply to the typing contexts;
  moreover, typing constraints on usage annotations cannot always be eagerly solved in open processes.

  We approach the first challenge using co-contextual type inference, where processes are traversed bottom-up and constraints are collected (and when possible eagerly solved) and merged on context splits.
  We approach the latter challenge by allowing the resolution of some of the constraints to be deferred, and adapting the soundness and completeness theorems to take this into account.
  We mechanise all our work in Agda.
\end{abstract}

\maketitle

\section{Introduction}\label{introduction}

\cite{ErdwegBKKM15}

@@

\bibliographystyle{abbrvnat}
\bibliography{paper}
\end{document}
